Estimating the Effect of Urban Green Spaces on Residential House Prices in Amsterdam

### 2023-04-13 Paper/Term Project - Grings, Nauta, Nibbering.Rmd
paper update

```{=latex}
\begin{table*}[]
\centering
\caption{Descriptive Statistics of Property, Public Amenity and Greenness Characteristics of Properties in  Amsterdam.}
\begin{tabular}{@{}llll@{}}
\toprule
\textbf{Independent Variable}      & \textbf{Mean} & \textbf{SD} & \textbf{Description}                        \\ \midrule
\multicolumn{4}{c}{\textbf{Summary Statistics (N = 1,719)}}                                                    \\ \midrule
\textbf{Property Characteristics$^1$}  &               &             &                                             \\
Living Area (m2) [38]                   & 105.7         & 71.0        & Size of livable area of the property        \\
Number of Bedrooms [38, 39]                & 2.5           & 1.4         & Number of bedrooms of the property          \\
Number of Bathrooms [23]               & 1.1           & 0.7         & Number of bathrooms of the property         \\
House Age (years) [23, 38]            & 76.9          & 63.2        & Age of the property in 2023                 \\
\textbf{Design$^2$}                    &               &             &                                             \\
NDVI$_{100}$ [36, 39, 40]                & 0.200         & 0.073       & Average NDVI at 100 m around property       \\
NDVI$_{300}$ [36, 39, 40]                & 0.212         & 0.069       & Average NDVI at 300 m around property       \\
NDVI$_{500}$ [36, 39, 40]               & 0.216         & 0.067       & Average NDVI at 500 m around property       \\
\textbf{Transit Distance$^{3,4,5}$} &               &             &                                             \\
Distance to Train Station (m) [22]     & 1703.7        & 958.2       & Euclidean distance to nearest train station \\
Distance to Tram Station (m) [22]      & 689.1         & 1024.7      & Euclidean distance to nearest tram station  \\
Distance to Metro Station (m) [23]      & 1303.2        & 951.8       & Euclidean distance to nearest metro station \\
\textbf{Destination Accessibility$^4$} &               &             &                                             \\
Distance to City Center (m) [38]       & 3770.5        & 2288.1      & Euclidean distance to city center           \\
Distance to Business District (m) [38] & 4659.2 & 2228.3 & Euclidean distance to business district \\
Distance to School (m) [23]            & 268.3         & 183.8       & Euclidean distance to nearest school        \\
Distance to Convenience Stores (m) [38] & 266.7         & 206.9       & Euclidean distance to nearest store         \\ \bottomrule
\multicolumn{4}{l}{Sources: $^1$Funda.nl, $^2$Sentinel-2, $^3$ArcGIS, $^4$OpenStreetMap.org, and $^5$Amsterdam Municipality} 
\end{tabular} 
\end{table*}
```

@@

```{=latex}
\begin{figure}[]
  \centering
  \includegraphics[width=\linewidth]{figures/Economic_Value_Urban_Green_clip.png}
  \caption{Overview of Statistically Significant Urban Green Space Coefficients, i.e. NDVI at a 300m Spatial Scale, (p < 0.05) in Amsterdam.}
\end{figure}
```

@@

```{=latex}
\begin{table*}[ht]
\centering
\caption{Coefficients and Statistical Significance of the Ordinary Least Squares and Geographically Weighted Regression Models.}
\begin{tabular}{@{}lllll@{}}
\toprule
\textbf{Independent Variable} &
  \textbf{Coef.} &
  \textbf{Min. Coef.} &
  \textbf{Median Coef.} &
  \textbf{Max. Coef.} \\ \midrule
                                     & OLS$^1$ &           & GWR$^{1,2}$ &           \\ \midrule
\textbf{Property Characteristics}    &            &           &         &           \\
Living Area (m2)                     & 4.7**      & -45.7     & -5.3    & 28.4      \\
Number of Bedrooms                   & -329.6**   & -1384.2   & -136.0  & 957.8     \\
Number of Bathrooms                  & 318.3**    & -1206.8   & 248.3   & 2,385.9   \\
House Age (years)                    & 1.3**      & -121.1    & -0.6    & 74.1      \\
\textbf{Design}                      &            &           &         &           \\
NDVI$_{300}$                              & -1,674.1** & -82,657.5 & 262.5   & 125,978.4 \\
\textbf{Transit Distance}            &            &           &         &           \\
Distance to Train Station (m)        & -0.08      & -79.7     & 1.0     & 297.5     \\
Distance to Tram Station (m)         & 0.4**      & -38.5     & 0.2     & 45.8      \\
Distance to Metro Station (m)        & 0.5**      & -66.0     & 0.5     & 39.1      \\
\textbf{Destination Accessibility}   &            &           &         &           \\
Distance to City Center (m)          & -0.5**     & -495.3    & -1.2    & 124.4     \\
Distance to Business District   (m)  & -0.5**     & -145.6    & -0.02   & 162.1     \\
Distance to School (m)               & 0.3        & -21.5     & -0.6    & 9.4       \\
Distance to Convenience Stores   (m) & 1.2**      & -15.4     & 0.2     & 18.1      \\ \midrule
Akaike Information Criterion   (AIC) & 30,487     &           & 29,720  &           \\ \midrule
\multicolumn{5}{l}{** Significant at p \textless 0.05}                              \\
\multicolumn{5}{l}{$^1$ Statistical significance levels are only reported for the global OLS model,} \\
\multicolumn{5}{l}{as p-values could not be easily presented for GWR due to its local approach.} \\
\multicolumn{5}{l}{$^2$ Bandwidth of adjusted kernel corresponds to 67.}              
\end{tabular}
\end{table*}
```

@@

```{=latex}
\begin{figure}[ht]
  \centering
  \includegraphics[width=.8\linewidth]{figures/NDVI_clip.png}
  \caption{Overview of Greenness Measurements in the Form of NDVI across the City of Amsterdam.}
\end{figure}
```

>>>>

```{=latex}
\begin{table*}[]
\centering
\caption{Descriptive statistics of property characteristics, public amenities and greenness measures of Amsterdam real-estate.}
\begin{tabular}{@{}llll@{}}
\toprule
\textbf{Independent Variable}      & \textbf{Mean} & \textbf{SD} & \textbf{Description}                        \\ \midrule
\multicolumn{4}{c}{\textbf{Summary Statistics (N = 1,719)}}                                                    \\ \midrule
\textbf{Property Characteristics$^1$}  &               &             &                                             \\
Living Area (m2) [38]                   & 105.7         & 71.0        & Size of livable area of the property        \\
Number of Bedrooms [38, 39]                & 2.5           & 1.4         & Number of bedrooms of the property          \\
Number of Bathrooms [23]               & 1.1           & 0.7         & Number of bathrooms of the property         \\
House Age (years) [23, 38]            & 76.9          & 63.2        & Age of the property in 2023                 \\
\textbf{Design$^2$}                    &               &             &                                             \\
NDVI$_{100}$ [36, 39, 40]                & 0.200         & 0.073       & Average NDVI at 100 m around property       \\
NDVI$_{300}$ [36, 39, 40]                & 0.212         & 0.069       & Average NDVI at 300 m around property       \\
NDVI$_{500}$ [36, 39, 40]               & 0.216         & 0.067       & Average NDVI at 500 m around property       \\
\textbf{Transit Distance$^{3,4,5}$} &               &             &                                             \\
Distance to Train Station (m) [22]     & 1703.7        & 958.2       & Euclidean distance to nearest train station \\
Distance to Tram Station (m) [22]      & 689.1         & 1024.7      & Euclidean distance to nearest tram station  \\
Distance to Metro Station (m) [23]      & 1303.2        & 951.8       & Euclidean distance to nearest metro station \\
\textbf{Destination Accessibility$^4$} &               &             &                                             \\
Distance to City Center (m) [38]       & 3770.5        & 2288.1      & Euclidean distance to city center           \\
Distance to Business District (m) [38] & 4659.2 & 2228.3 & Euclidean distance to business district \\
Distance to School (m) [23]            & 268.3         & 183.8       & Euclidean distance to nearest school        \\
Distance to Convenience Stores (m) [38] & 266.7         & 206.9       & Euclidean distance to nearest store         \\ \bottomrule
\multicolumn{4}{l}{Sources: $^1$Funda.nl, $^2$Sentinel-2, $^3$ArcGIS, $^4$OpenStreetMap.org, and $^5$Amsterdam Municipality} 
\end{tabular} 
\end{table*}
```

@@

```{=latex}
\begin{figure}[]
  \centering
  \includegraphics[width=\linewidth]{figures/Economic_Value_Urban_Green_clip.png}
  \caption{Overview of statistically significant (p < 0.05) urban green space coefficients at a 300m spatial scale in Amsterdam.}
\end{figure}
```

@@

```{=latex}
\begin{table*}[ht]
\centering
\caption{Coefficients and statistical significance of the Ordinary Least Squares and Geographically Weighted Regression models.}
\begin{tabular}{@{}lllll@{}}
\toprule
\textbf{Independent Variable} &
  \textbf{Coef.} &
  \textbf{Min. Coef.} &
  \textbf{Median Coef.} &
  \textbf{Max. Coef.} \\ \midrule
                                     & OLS$^1$ &           & GWR$^{1,2}$ &           \\ \midrule
\textbf{Property Characteristics}    &            &           &         &           \\
Living Area (m2)                     & 4.7**      & -45.7     & -5.3    & 28.4      \\
Number of Bedrooms                   & -329.6**   & -1384.2   & -136.0  & 957.8     \\
Number of Bathrooms                  & 318.3**    & -1206.8   & 248.3   & 2,385.9   \\
House Age (years)                    & 1.3**      & -121.1    & -0.6    & 74.1      \\
\textbf{Design}                      &            &           &         &           \\
NDVI$_{300}$                              & -1,674.1** & -82,657.5 & 262.5   & 125,978.4 \\
\textbf{Transit Distance}            &            &           &         &           \\
Distance to Train Station (m)        & -0.08      & -79.7     & 1.0     & 297.5     \\
Distance to Tram Station (m)         & 0.4**      & -38.5     & 0.2     & 45.8      \\
Distance to Metro Station (m)        & 0.5**      & -66.0     & 0.5     & 39.1      \\
\textbf{Destination Accessibility}   &            &           &         &           \\
Distance to City Center (m)          & -0.5**     & -495.3    & -1.2    & 124.4     \\
Distance to Business District   (m)  & -0.5**     & -145.6    & -0.02   & 162.1     \\
Distance to School (m)               & 0.3        & -21.5     & -0.6    & 9.4       \\
Distance to Convenience Stores   (m) & 1.2**      & -15.4     & 0.2     & 18.1      \\ \midrule
Akaike Information Criterion   (AIC) & 30,487     &           & 29,720  &           \\ \midrule
\multicolumn{5}{l}{** Significant at p \textless 0.05}                              \\
\multicolumn{5}{l}{$^1$ Statistical significance levels are only reported for the global OLS model,} \\
\multicolumn{5}{l}{as p-values could not be easily presented for GWR due to its local approach.} \\
\multicolumn{5}{l}{$^2$ Bandwidth of adjusted kernel corresponds to 67.}              
\end{tabular}
\end{table*}
```

@@

```{=latex}
\begin{figure}[ht]
  \centering
  \includegraphics[width=.8\linewidth]{figures/NDVI_clip.png}
  \caption{Overview of NDVI values in Amsterdam with a 300m Spatial Scale}
\end{figure}
```
